\documentclass[../main.tex]{subfiles}

\begin{document}

% 中文摘要
\begin{titlepage}

    \pagestyle{empty}

    \begin{spacing}{1.05}
        \centering
        \parbox[c]{.75\textwidth}{
          \centering
          \heiti\zihao{3}\textbf{\thesistitle}
        }
    \end{spacing}

    \begin{spacing}{1.5}
        \centering
        \zihao{-3}\quad{} \\ 
        \heiti\zihao{-3}\textbf{摘\quad{}要} \\ 
    \end{spacing}
    \zihao{-3}\quad{}

    \normalsize

    本科毕业设计（论文）是本科专业培养方案的重要组成部分，是人才培养的关键环节，是实现教学、科研与社会实践相结合的重要结合点。为全面贯彻党的教育方针，围绕立德树人根本任务，构建面向产出的本科毕业设计（论文）管理体系，提高人才培养质量，进一步加强我校毕业设计（论文）教学管理，依据《北京邮电大学本科毕业设计（论文）管理办法》（校发〔2023〕14 号）《北京邮电大学本科毕业设计（论文）质量管理实施细则（试行）》（党政办发〔2023〕14 号）等相关文件要求，特制定 2025 届本科毕业设计（论文）指导手册。

    现参照2025 届本科毕业设计（论文）指导手册制作毕业设计论文模板。

    \quad{}

    \par\noindent\heiti\zihao{-4}\textbf{关键词}\quad{}
    {
      \songti\zihao{-4}
      毕业设计\quad
      论文模板\quad
      Latex\quad
    } 
\end{titlepage}

\thispagestyle{empty}

% 英文摘要
\begin{titlepage}

    \pagestyle{empty}

    \begin{spacing}{1.05}
        \centering
        % 如果你的标题太长，可能会换行；如果你对换行位置不满意，请调节下面第一个{}的参数
        \parbox[c]{.75\textwidth}{
          \centering
          \zihao{3}\textbf{\thesisenglishtitle}
        }
    \end{spacing}

    \begin{spacing}{1.5}
        \centering
        \zihao{-3}\quad \\ 
        \zihao{-3}\textbf{ABSTRACT} \\ 
    \end{spacing}
    \zihao{-3}\quad

    \normalsize

    The final project (dissertation) is an important part of the undergraduate professional training program and a key link in talent cultivation. It is an important convergence point for integrating teaching, scientific research, and social practice. To comprehensively implement the Party's educational principles and fulfill the fundamental task of cultivating people with integrity, Beijing University of Posts and Telecommunications (BUPT) has established a graduation project (dissertation) management system oriented towards output to enhance the quality of talent cultivation. In order to further strengthen the management of graduation project (dissertation) teaching at BUPT, this manual is formulated based on the relevant documents, including the \textit{Regulations on the Management of Undergraduate Final Projects (Dissertations) at Beijing University of Posts and Telecommunications} (No. 14, School of BUPT, 2023) and the \textit{Implementation Rules for Quality Management of Undergraduate Final Projects (Dissertations) at Beijing University of Posts and Telecommunications (for Trial Implementation)} (No. 14, Office of the Party Committee and the Office of the President, BUPT, 2023), etc. 

    Now, we are referring to the 2025 Graduation Thesis (Paper) Guidance Manual to create a template for graduation thesis papers.

    \quad{}

    \par\noindent\zihao{-4}\textbf{KEY WORDS}\quad{}%
    {
      \zihao{-4}
      Graduate Design\quad
      Thesis Template\quad
      Latex\quad
    }

\end{titlepage}

\thispagestyle{empty}

\end{document}
